---
title: "Tree_Data"
output: html_document
date: "2024-02-05"
---

** About the Data ** 

Detailed information about each column follows:

No: Seedling unique ID number.
Plot: Number of the field plot the seedling was planted in (1-18).
Subplot: Subplot within the main plot the seedling was planted in. Broken into 5 subplots (1 per corner, plus 1 in the middle) (A-E).
Species: Includes Acer saccharum, Prunus serotina, Quercus alba, and Quercus rubra.
Light ISF: Light level quantified with HemiView software. Represents the amount of light reaching each subplot at a height of 1m.
Light Cat: Categorical light level created by splitting the range of Light_ISF values into three bins (low, med, high).
Core: Year the soil core was removed from the field.
Soil: Species from which the soil core was taken. Includes all species, plus Acer rubrum, Populus grandidentata, and a sterilized conspecific for each species.
Adult: Individual tree that soil was taken from. Up to 6 adults per species. Used as a random effect in analyses.
Sterile: Whether the soil was sterilized or not.
Conspecific: Whether the soil was conspecific, heterospecific, or sterilized conspecific.
Myco: Mycorrhizal type of the seedling species (AMF or EMF).
SoilMyco: Mycorrhizal type of the species culturing the soil (AMF or EMF).
PlantDate: The date that seedlings were planted in the field pots.
AMF: Percent arbuscular mycorrhizal fungi colonization on the fine roots of harvested seedlings.
EMF: Percent ectomycorrhizal fungi colonization on the root tips of harvested seedlings.
Phenolics: Calculated as nmol Gallic acid equivalents per mg dry extract (see manuscript for detailed methods).
NSC: Calculated as percent dry mass nonstructural carbohydrates (see manuscript for detailed methods).
Lignin: Calculated as percent dry mass lignin (see manuscript for detailed methods).
Census: The census number at which time the seedling died or was harvested.
Time: The number of days at which time the seedling died or was harvested.
Event: Used for survival analysis to indicate status of each individual seedling at a given time (above)
0 = harvested or experiment ended
1 = dead
Harvest: Indicates whether the seedling was harvested for trait measurement.
Alive: Indicates if the seedling was alive at the end of the second growing season. "X" in this field indicates alive status.

## Load the libraries 
```{r }
library(tidyverse)
library(ggplot2)
library(dplyr)
library(readr)
```


## Load the data 
```{r }
treedata<- read.csv("Tree_Data.csv", header=TRUE, na.strings= "NA")
str(treedata)

```

## check for na 

```{r }
colSums(is.na(treedata))

```
```{r}
job<- read.csv("fake_job_postings.csv", header = TRUE,  na.strings = "")
colSums(is.na(job))
dim(job)
```

```{r}
Cirrhosis_Data<- read.csv("cirrhosis.csv", header=TRUE, na.strings= "NA")
colSums(is.na(Cirrhosis_Data))
dim(Cirrhosis_Data)
```


