---
title: "Tree_Data"
output: html_document
date: "2024-02-05"
---

** About the Data ** 

Detailed information about each column follows:

No: Seedling unique ID number.
Plot: Number of the field plot the seedling was planted in (1-18).
Subplot: Subplot within the main plot the seedling was planted in. Broken into 5 subplots (1 per corner, plus 1 in the middle) (A-E).
Species: Includes Acer saccharum, Prunus serotina, Quercus alba, and Quercus rubra.
Light ISF: Light level quantified with HemiView software. Represents the amount of light reaching each subplot at a height of 1m.
Light Cat: Categorical light level created by splitting the range of Light_ISF values into three bins (low, med, high).
Core: Year the soil core was removed from the field.
Soil: Species from which the soil core was taken. Includes all species, plus Acer rubrum, Populus grandidentata, and a sterilized conspecific for each species.
Adult: Individual tree that soil was taken from. Up to 6 adults per species. Used as a random effect in analyses.
Sterile: Whether the soil was sterilized or not.
Conspecific: Whether the soil was conspecific, heterospecific, or sterilized conspecific.
Myco: Mycorrhizal type of the seedling species (AMF or EMF).
SoilMyco: Mycorrhizal type of the species culturing the soil (AMF or EMF).
PlantDate: The date that seedlings were planted in the field pots.
AMF: Percent arbuscular mycorrhizal fungi colonization on the fine roots of harvested seedlings.
EMF: Percent ectomycorrhizal fungi colonization on the root tips of harvested seedlings.
Phenolics: Calculated as nmol Gallic acid equivalents per mg dry extract (see manuscript for detailed methods).
NSC: Calculated as percent dry mass nonstructural carbohydrates (see manuscript for detailed methods).
Lignin: Calculated as percent dry mass lignin (see manuscript for detailed methods).
Census: The census number at which time the seedling died or was harvested.
Time: The number of days at which time the seedling died or was harvested.
Event: Used for survival analysis to indicate status of each individual seedling at a given time (above)
0 = harvested or experiment ended
1 = dead
Harvest: Indicates whether the seedling was harvested for trait measurement.
Alive: Indicates if the seedling was alive at the end of the second growing season. "X" in this field indicates alive status.

## Load the libraries 
```{r }
library(tidyverse)
library(ggplot2)
library(dplyr)
library(readr)
```


## Load the data 
```{r }
treedata<- read.csv("Tree_Data.csv", header=TRUE, na.strings= "NA")
str(treedata)

```

## check for na 

```{r }
colSums(is.na(treedata))

```
```{r}
job<- read.csv("fake_job_postings.csv", header = TRUE,  na.strings = "")
colSums(is.na(job))
dim(job)
```

```{r}
Cirrhosis_Data<- read.csv("cirrhosis.csv", header=TRUE, na.strings= "NA")
colSums(is.na(Cirrhosis_Data))
dim(Cirrhosis_Data)
```
## check for na 

```{r }
colSums(is.na(treedata))

```
```{r}
treedata$PlantDate <- as.Date(treedata$PlantDate, format = "%m/%d/%y")
```
```{r}
treedata$Subplot <- as.factor(treedata$Subplot)
```

```{r}
summary(treedata$AMF)
boxplot(treedata$AMF)
```

```{r}
treedata<- treedata[ ,-16]
```

```{r}
treedata<- treedata[ ,-22:-23]
```
```{r}
str(treedata)
```

```{r}
treedata$Event<- factor(treedata$Event)
str(treedata$Event)
```
```{r}
glimpse(treedata)
```
#Exploring categorical values 
table(treedata$Species)
table(treedata$Light_Cat)
table(treedata$Soil)
table(treedata$Sterile)
table(treedata$Conspecific)
table(treedata$Myco)
table(treedata$SoilMyco)
table(treedata$Event)


```{r}
# Histogram of Light_ISF
hist(treedata$Light_ISF, main = "Distribution of Light_ISF", xlab = "Light_ISF")



```

```{r}
# Boxplot of AMF by Species
boxplot(AMF ~ Species, data = treedata, main = "AMF by Species", xlab = "Species", ylab = "AMF")


```

# Scatterplot of Phenolics and Lignin
plot(treedata$Phenolics, treedata$Lignin, main = "Phenolics vs. Lignin", xlab = "Phenolics", ylab = "Lignin")


```

# Scatterplot of NSC and Light_ISF
plot(treedata$NSC, treedata$Light_ISF, main = "NSC vs. Light_ISF", xlab = "NSC", ylab = "Light_ISF")
```
```{r}
barplot(table(treedata$Species, treedata$Census), beside = TRUE, 
        main = "Census Counts by Species", xlab = "Species", ylab = "Count", 
        legend = rownames(table(treedata$Species, treedata$Census)))

```

library(ggplot2)
ggplot(treedata, aes(x = Time, fill = Event)) +
  geom_density(alpha = 0.5) +
  labs(title = "Density Plot of Time by Event", x = "Time", y = "Density") +
  theme_minimal()

```

```{r}
boxplot(treedata[, c("AMF", "Phenolics", "Lignin", "NSC")], col = rainbow(4),
        main = "Boxplot Matrix of Key Variables")

```

```{r}
pairs(treedata[, c("AMF", "Phenolics", "Lignin", "NSC")], 
      main = "Scatterplot Matrix of Key Variables")

```
```{r}
correlation_matrix <- cor(treedata[, c("AMF", "Phenolics", "Lignin", "NSC")])
corrplot::corrplot(correlation_matrix, method = "color", type = "upper", 
                   addCoef.col = "black", tl.col = "black", tl.srt = 45)

```




